\documentclass[12pt]{article}

\usepackage{physics}


\usepackage{tikz} % картинки в tikz
\usepackage{microtype} % свешивание пунктуации

\usepackage{array} % для столбцов фиксированной ширины

\usepackage{indentfirst} % отступ в первом параграфе

\usepackage{sectsty} % для центрирования названий частей
\allsectionsfont{\centering}

\usepackage{amsmath, amsfonts, amssymb} % куча стандартных математических плюшек

\usepackage{comment}

\usepackage[top=2cm, left=1.2cm, right=1.2cm, bottom=2cm]{geometry} % размер текста на странице

\usepackage{lastpage} % чтобы узнать номер последней страницы

\usepackage{enumitem} % дополнительные плюшки для списков
%  например \begin{enumerate}[resume] позволяет продолжить нумерацию в новом списке
\usepackage{caption}

\usepackage{url} % to use \url{link to web}

\usepackage{fancyhdr} % весёлые колонтитулы
\pagestyle{fancy}
\lhead{}
\chead{}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}



\usepackage{todonotes} % для вставки в документ заметок о том, что осталось сделать
% \todo{Здесь надо коэффициенты исправить}
% \missingfigure{Здесь будет Последний день Помпеи}
% \listoftodos - печатает все поставленные \todo'шки


% более красивые таблицы
\usepackage{booktabs}
% заповеди из докупентации:
% 1. Не используйте вертикальные линни
% 2. Не используйте двойные линии
% 3. Единицы измерения - в шапку таблицы
% 4. Не сокращайте .1 вместо 0.1
% 5. Повторяющееся значение повторяйте, а не говорите "то же"



\usepackage{fontspec}
\usepackage{polyglossia}

\setmainlanguage{english}
\setotherlanguages{english}

% download "Linux Libertine" fonts:
% http://www.linuxlibertine.org/index.php?id=91&L=1
\setmainfont{Linux Libertine O} % or Helvetica, Arial, Cambria
% why do we need \newfontfamily:
% http://tex.stackexchange.com/questions/91507/
\newfontfamily{\cyrillicfonttt}{Linux Libertine O}

%\AddEnumerateCounter{\asbuk}{\russian@alph}{щ} % для списков с русскими буквами
%\setlist[enumerate, 2]{label=\asbuk*),ref=\asbuk*}

%% эконометрические сокращения
\DeclareMathOperator{\Cov}{\mathbb{C}ov}
\DeclareMathOperator{\Corr}{\mathbb{C}orr}
\DeclareMathOperator{\Var}{\mathbb{V}ar}

\let\P\relax
\DeclareMathOperator{\P}{\mathbb{P}}

\DeclareMathOperator{\E}{\mathbb{E}}
% \DeclareMathOperator{\tr}{trace}
\DeclareMathOperator{\card}{card}
\DeclareMathOperator{\pCorr}{\mathrm{p}\mathbb{C}\mathrm{orr}}


\newcommand \hb{\hat{\beta}}
\newcommand \hs{\hat{\sigma}}
\newcommand \htheta{\hat{\theta}}
\newcommand \s{\sigma}
\newcommand \hy{\hat{y}}
\newcommand \hY{\hat{Y}}
\newcommand \e{\varepsilon}
\newcommand \he{\hat{\e}}
\newcommand \z{z}
\newcommand \hVar{\widehat{\Var}}
\newcommand \hCorr{\widehat{\Corr}}
\newcommand \hCov{\widehat{\Cov}}
\newcommand \cN{\mathcal{N}}
\newcommand \RR{\mathbb{R}}
\newcommand \NN{\mathbb{N}}
\newcommand{\cF}{\mathcal{F}}
\newcommand{\cH}{\mathcal{H}}


\begin{document}



\section*{Reply to the provisional acceptance letter}

Primary subject: 60C05. Secondary subject: 11B37.

I have incorporated all the proposed changes. Only two points are not clear to me. 

\begin{enumerate}
  \item \textit{Please enter the correct reference number here or compile the 
  TeX file before submitting. Here and elsewhere.}

  On my local computer the pdf is compiled with correct reference numbers.
  The [?] sign is the result of one-pass auto-compile of the tex file uploaded. 
  
  In the big commented submission pdf one may see that the first included version on page 4 (auto-compiled from tex) has [?] 
  signs but the second version on page 6 (compiled on my computer) is ok.
  
  What should I do?

  \item \textit{This Filler may be a bit too long. 
  You may need to remove one sentence. We can wait and see if you prefer.}

  If the length is ok then I prefer to keep everything. If the filler is too long 
  then I am ready to sacrifice the following passage:

\begin{quote}
  This property of geometric series also has an economic intuition. 
Your final welfare $b_k$ equals your initial welfare $b_1$ plus all interest payments,
where $\alpha$ is the nominal rate of compound interest.
\end{quote}

\end{enumerate}



\textit{Below is the content of the past cover letters:}


\section*{Reply to the referee (2021-08-30)}

\begin{enumerate}
  \item Totally agree. Updated the text.
  \item Partially agree. However I think that numbering equation in a very short filler is too much.
  So I replaced the proposed (1) by (the geometric series equation).
  \item Totally agree. Updated the text.
  \item Not needed as the filler still fits one page limit after modifications.
\end{enumerate}


\section*{Original cover letter (2021-08-25)}

A simplier (I hope) proof of a more general result about 
expected number of dice rolls than in \url{https://www.tandfonline.com/doi/full/10.1080/00029890.2020.1693213}.

The list of submitted files:
\begin{itemize}
  \item \verb|filler-nsided.tex|: the main tex file.
  \item \verb|filler-nsided.pdf|: compiled pdf.
  \item \verb|geometric_series.png|: the picture. The corresponding tikz-code is commented out in the tex file. 
\end{itemize}





\end{document}

